Capon Beamforming and Moving Objects - An Analysis of Lateral Shift-Invariance

### 2014-03-04 HRUIofMovingObjects/jrnl_article.tex
Changed back to draft style.

% Note that the a4paper option is mainly intended so that authors in
% countries using A4 can easily print to A4 and see how their papers will
% look in print - the typesetting of the document will not typically be
% affected with changes in paper size (but the bottom and side margins will).
% Use the testflow package mentioned above to verify correct handling of
% both paper sizes by the user's LaTeX system.
%
% Also note that the "draftcls" or "draftclsnofoot", not "draft", option
% should be used if it is desired that the figures are to be displayed in
% draft mode.
%
%\documentclass[draftcls]{IEEEtran}
\documentclass[journal]{IEEEtran}
%
% If IEEEtran.cls has not been installed into the LaTeX system files,
% manually specify the path to it like:
% \documentclass[journal]{../sty/IEEEtran}

@@

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{photos/sverre.eps}}]{Sverre Holm}
(M’82-SM’02) was born in Oslo, Norway, in 1954. He received the M.S. and Ph.D. degrees in electrical engineering from the Norwegian Institute of Technology, Trondheim, in 1978 and 1982, respectively. His academic experience includes Yarmouk University in Jordan (1984-1986) and the Norwegian Institute of Technology and later the University of Oslo (1989-1994) as an adjunct professor. Since 1995, he has been a professor of signal processing in the Department of Informatics at the University of Oslo. In 2002, he was elected a member of the Norwegian Academy of Technological Sciences, and in 2009, he became an adjunct professor in the Norwegian University of Science and Technology (NTNU) Medical Imaging Lab, Trondheim. His industry experience includes GE Vingmed Ultrasound, Horten, Norway (1990-1994). He worked with Sonitor Technologies (2000-2005), where he developed ultrasonic technology that is the core of the indoor positioning system described in \textit{Scientific Americanin} 2008 as "a positioning system that goes where GPS can't." He has published about 130 publications internationally, plus about 10 patents. He has had sabbaticals at GE Global Research, NY (1998), and the Waves and Acoustics Laboratory of ESPCI, Paris (2008-2009). He was an associate editor of the \textit{IEEE Transactions on Ultrasonics, Ferroelectrics, and Frequency Control} from 1997 to 2002. His research interests are medical ultrasound imaging, modeling of tissue-ultrasound interaction, and ultrasound positioning.
\end{IEEEbiography}

>>>>

% Note that the a4paper option is mainly intended so that authors in
% countries using A4 can easily print to A4 and see how their papers will
% look in print - the typesetting of the document will not typically be
% affected with changes in paper size (but the bottom and side margins will).
% Use the testflow package mentioned above to verify correct handling of
% both paper sizes by the user's LaTeX system.
%
% Also note that the "draftcls" or "draftclsnofoot", not "draft", option
% should be used if it is desired that the figures are to be displayed in
% draft mode.
%
\documentclass[draftcls]{IEEEtran}
%\documentclass[journal]{IEEEtran}
%
% If IEEEtran.cls has not been installed into the LaTeX system files,
% manually specify the path to it like:
% \documentclass[journal]{../sty/IEEEtran}

@@

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{photos/sverre.eps}}]{Sverre Holm}
(M82-SM02) was born in Oslo, Norway, in 1954. He received the M.S. and Ph.D. degrees in electrical engineering from the Norwegian Institute of Technology, Trondheim, in 1978 and 1982, respectively. His academic experience includes Yarmouk University in Jordan (1984-1986) and the Norwegian Institute of Technology and later the University of Oslo (1989-1994) as an adjunct professor. Since 1995, he has been a professor of signal processing in the Department of Informatics at the University of Oslo. In 2002, he was elected a member of the Norwegian Academy of Technological Sciences, and in 2009, he became an adjunct professor in the Norwegian University of Science and Technology (NTNU) Medical Imaging Lab, Trondheim. His industry experience includes GE Vingmed Ultrasound, Horten, Norway (1990-1994). He worked with Sonitor Technologies (2000-2005), where he developed ultrasonic technology that is the core of the indoor positioning system described in \textit{Scientific Americanin} 2008 as "a positioning system that goes where GPS can't." He has published about 130 publications internationally, plus about 10 patents. He has had sabbaticals at GE Global Research, NY (1998), and the Waves and Acoustics Laboratory of ESPCI, Paris (2008-2009). He was an associate editor of the \textit{IEEE Transactions on Ultrasonics, Ferroelectrics, and Frequency Control} from 1997 to 2002. His research interests are medical ultrasound imaging, modeling of tissue-ultrasound interaction, and ultrasound positioning.
\end{IEEEbiography}
